Refunctionalization of Abstract Abstract Machines (Functional Pearl)

### 2018-03-17 paper.tex
pass over intro

Pushdown control flow analysis (PDCFA) is another mechanism which maintains this precision 
through the use of a specialized state graph representing all possible stacks contained 
within the unbounded-stack machine. These state graphs are known as Dyke state graphs.

>>>>

As mentioned in Section~\ref{unabs}, maintaining the perfect precision provided by an unbounded-stack machine is essential when performing the proposed transformations. Pushdown control flow analysis (PDCFA) is a mechanism which maintains this precision through the use of a specialized state graph representing all possible stacks contained within the unbounded-stack machine. These state graphs are known as \emph{Dyke state graphs}~\cite{gilray2016pushdown}.
